The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
add net mets package cites
rm "habitat types"

## Landscape data and habitat classification
<!-- TODO: update citation for lc product from Hance -->
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at 30 m
resolution. We reclassified the landcover types into three categories: foraging
habitat, open habitat, and forest habitat using the R package `raster`
[@Hijmans_2019]. Foraging habitat consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest habitat types. Water habitat was excluded from all
subsequent analyses.

@@

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and landcover context <!-- TODO: citation for
graph strength?-->. Extending degree centrality, we calculated multidegree, the
sum of degree centrality across layers, and neighbourhood, the sum of unique
neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate connective redundancy and layer relevance. Connective
redundancy is the proportion of neighbours repeated in multiple layers, and
layer relevance is the proportion of neighbours present in each layer compared
to the neighbourhood for each individual [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across landcover classes
(e.g. winter open compared to summer open) using the Pearson correlation
coefficient [@Br_dka_2018].

>>>>

## Landscape data and habitat classification
<!-- TODO: update citation for lc product from Hance -->
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at 30 m
resolution. We reclassified the landcover types into three categories: foraging
habitat, open habitat, and forest habitat using the R package `raster`
[@Hijmans_2019]. Foraging habitat consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.

@@

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and landcover context <!-- TODO: citation for
graph strength?-->. Extending degree centrality, we calculated multidegree, the
sum of degree centrality across layers, and neighbourhood, the sum of unique
neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate connective redundancy and layer relevance. Connective
redundancy is the proportion of neighbours repeated in multiple layers, and
layer relevance is the proportion of neighbours present in each layer compared
to the neighbourhood for each individual [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across landcover classes
(e.g. winter open compared to summer open) using the Pearson correlation
coefficient [@Br_dka_2018]. Network metrics were calculated using the R packages 
`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
